\begin{thebibliography}{99}

\bibitem{zheng2023judging}
Lianmin Zheng, Wei-Lin Chiang, Ying Sheng, Siyuan Zhuang, Zhanghao Wu, Yonghao Zhuang, Zi Lin, Zhuohan Li, Dacheng Li, Eric~P. Xing, Hao Zhang, Joseph~E. Gonzalez, and Ion Stoica.
\newblock Judging {LLM}-as-a-judge with {MT-Bench} and {Chatbot Arena}.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem{wang2022selfinstruct}
Yizhong Wang, Yeganeh Kordi, Swaroop Mishra, Alisa Liu, Noah~A. Smith, Daniel Khashabi, and Hannaneh Hajishirzi.
\newblock Self-instruct: Aligning language models with self-generated instructions.
\newblock \emph{arXiv preprint arXiv:2212.10560}, 2022.

\bibitem{deng2023mind2web}
Xiang Deng, Yu Gu, Boyuan Zheng, Shijie Chen, Samuel Stevens, Boshi Wang, Huan Sun, and Yu Su.
\newblock {Mind2Web}: Towards a generalist agent for the web.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem{liu2023agentbench}
Xiao Liu, Hao Yu, Hanchen Zhang, Yifan Xu, Xuanyu Lei, Hanyu Lai, Yu Gu, Hangliang Ding, Kaiwen Men, Kejuan Yang, Shudan Zhang, Xiang Deng, Aohan Zeng, Zhengxiao Du, Chenhui Zhang, Sheng Shen, Tianjun Zhang, Yu Su, Huan Sun, Minlie Huang, Yuxiao Dong, and Jie Tang.
\newblock {AgentBench}: Evaluating {LLMs} as agents.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem{yang2023taobench}
Fan Yang, Jiazheng Li, Tianyu Zhao, Chao Yu, Lei Li, and Yue Zhang.
\newblock {TaoBench}: A task-oriented benchmark for evaluating large language model agents.
\newblock \emph{arXiv preprint arXiv:2311.18730}, 2023.

\bibitem{xu2024magpie}
Zhen Xu, Can Xu, Chongyang Tao, and Furu Wei.
\newblock Magpie: Alignment data synthesis from scratch by prompting aligned {LLMs} with nothing.
\newblock \emph{arXiv preprint arXiv:2402.04333}, 2024.

\bibitem{cui2024ultrafeedback}
Ganqu Cui, Lifan Yuan, Ning Ding, Guanming Yao, Wei Zhu, Yuan Ni, Guotong Xie, Zhiyuan Liu, and Maosong Sun.
\newblock {UltraFeedback}: Boosting language models with scaled {AI} feedback.
\newblock In \emph{International Conference on Machine Learning}, 2024.

\bibitem{zhou2024webarena}
Shuyan Zhou, Frank~F. Xu, Hao Zhu, Xuhui Zhou, Robert Lo, Abishek Sridhar, Xianyi Cheng, Tianyue Ou, Yonatan Bisk, Daniel Fried, Uri Alon, and Graham Neubig.
\newblock {WebArena}: A realistic web environment for building autonomous agents.
\newblock In \emph{International Conference on Learning Representations}, 2024.

\bibitem{drouin2024workarena}
Alexandre Drouin, Maxime Gasse, Massimo Caccia, Issam~H. Laradji, Manuel Del Verme, Tom Marty, L{\'e}o Boisvert, Megh Thakkar, Quentin Cappart, David Vazquez, Nicolas Chapados, and Alexandre Lacoste.
\newblock {WorkArena}: How capable are web agents at solving common knowledge work tasks?
\newblock In \emph{Conference on Empirical Methods in Natural Language Processing}, 2024.

\bibitem{trivedi2024appworld}
Harsh Trivedi, Tushar Khot, Mareike Hartmann, Ruskin Manku, Vinty Dong, Edward Li, Shashank Gupta, Ashish Sabharwal, and Niranjan Balasubramanian.
\newblock {AppWorld}: A controllable world of apps and people for benchmarking interactive coding agents.
\newblock In \emph{Proceedings of the 62nd Annual Meeting of the Association for Computational Linguistics}, 2024.

\bibitem{xu2025agenttrek}
Yiheng Xu, Dunjie Lu, Zhennan Shen, Junli Wang, Zekun Wang, Yuchen Mao, Caiming Xiong, and Tao Yu.
\newblock {AgentTrek}: Agent trajectory synthesis via guiding replay with web tutorials.
\newblock In \emph{International Conference on Learning Representations}, 2025.

\bibitem{patil2025bfcl}
Shishir~G. Patil, Huanzhi Mao, Charlie Cheng-Jie Ji, Fanjia Yan, Vishnu Suresh, Ion Stoica, and Joseph~E. Gonzalez.
\newblock The {Berkeley Function Calling Leaderboard (BFCL)}: From tool use to agentic evaluation of large language models.
\newblock In \emph{International Conference on Machine Learning}, 2025.

\bibitem{shen2024taskbench}
Yongliang Shen, Kaitao Song, Xu Tan, Wenqi Zhang, Kan Ren, Siyu Yuan, Weiming Lu, Dongsheng Li, and Yueting Zhuang.
\newblock {TaskBench}: Benchmarking large language models for task automation.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2024.

\bibitem{funcbenchgen2025}
Anonymous.
\newblock Towards reliable benchmarking: A contamination free, controllable evaluation framework for multi-step {LLM} function calling.
\newblock \emph{arXiv preprint arXiv:2509.26553}, 2025.

\bibitem{tan2024judgebench}
Yuanhe Tan, Minghao Liu, Yaozu Wu, and others.
\newblock {JudgeBench}: A benchmark for evaluating {LLM}-based judges.
\newblock In \emph{International Conference on Learning Representations}, 2025.

\bibitem{li2024arenahard}
Tianle Li, Wei-Lin Chiang, Evan Frick, Lisa Dunlap, Tianhao Wu, Banghua Zhu, Joseph~E. Gonzalez, and Ion Stoica.
\newblock From crowdsourced data to high-quality benchmarks: {Arena-Hard} and {BenchBuilder} pipeline.
\newblock \emph{arXiv preprint arXiv:2406.11939}, 2024.

\bibitem{wang2024pandalm}
Yidong Wang, Zhuohao Yu, Zhengran Zeng, Linyi Yang, Cunxiang Wang, Hao Chen, Chaoya Jiang, Rui Xie, Jindong Wang, Xing Xie, Wei Ye, Shikun Zhang, and Yue Zhang.
\newblock {PandaLM}: An automatic evaluation benchmark for {LLM} instruction tuning optimization.
\newblock In \emph{International Conference on Learning Representations}, 2024.

\bibitem{li2024autoj}
Junlong Li, Shichao Sun, Weizhe Yuan, Run-Ze Fan, Hai Zhao, and Pengfei Liu.
\newblock Generative judge for evaluating alignment.
\newblock In \emph{International Conference on Learning Representations}, 2024.

\bibitem{verga2024jury}
Pat Verga, Sebastian Hofst{\"a}tter, Sophia Althammer, Yixuan Su, Aleksandra Piktus, Arkady Arkhangorodsky, Minjie Xu, Naomi White, and Patrick Lewis.
\newblock Replacing judges with juries: Evaluating {LLM} generations with a panel of diverse models.
\newblock \emph{arXiv preprint arXiv:2404.18796}, 2024.

\bibitem{wang2024fair}
Peiyi Wang, Lei Li, Liang Chen, Dawei Zhu, Binghuai Lin, Yunbo Cao, Qi Liu, Tianyu Liu, and Zhifang Sui.
\newblock Large language models are not fair evaluators.
\newblock \emph{arXiv preprint arXiv:2305.17926}, 2024.

\bibitem{qin2023toolllm}
Yujia Qin, Shihao Liang, Yining Ye, Kunlun Zhu, Lan Yan, Yaxi Lu, Yankai Lin, Xin Cong, Xiangru Tang, Bill Qian, Sihan Zhao, Runchu Tian, Ruobing Xie, Jie Zhou, Mark Gerstein, Dahai Li, Zhiyuan Liu, and Maosong Sun.
\newblock {ToolLLM}: Facilitating large language models to master 16000+ real-world {APIs}.
\newblock In \emph{International Conference on Learning Representations}, 2024.

\bibitem{guo2024stabletoolbench}
Zhicheng Guo, Sijie Cheng, Hao Wang, Shihao Liang, Yujia Qin, Peng Li, Zhiyuan Liu, Maosong Sun, and Yang Liu.
\newblock {StableToolBench}: Towards stable large-scale benchmarking on tool learning of {LLMs}.
\newblock \emph{arXiv preprint arXiv:2403.07714}, 2024.

\bibitem{mcpagentbench2025}
Anonymous.
\newblock {MCP-AgentBench}: A benchmark for evaluating agents on {MCP} tool-use tasks.
\newblock \emph{arXiv preprint}, 2025.

\bibitem{krechetova2025geobenchx}
Varvara Krechetova and Denis Kochedykov.
\newblock {GeoBenchX}: Benchmarking {LLMs} in agent solving multistep geospatial tasks.
\newblock In \emph{Proceedings of the 1st ACM SIGSPATIAL International Workshop on Generative and Agentic AI for Multi-Modality Space-Time Intelligence}, 2025.

\bibitem{zhuge2024agentjudge}
Mingchen Zhuge, Changsheng Zhao, Dylan Ashley, Wenyi Wang, Dmitrii Khizbullin, Yunyang Xiong, Zechun Liu, Ernie Chang, Raghuraman Krishnamoorthi, Yuandong Tian, Yangyang Shi, Vikas Chandra, and J{\"u}rgen Schmidhuber.
\newblock Agent-as-a-judge: Evaluate agents with agents.
\newblock \emph{arXiv preprint arXiv:2410.10934}, 2024.

\bibitem{bhonsle2025autoeval}
Roshita Bhonsle, Rishav Dutta, Sneha Vavilapalli, Harsh Seth, Abubakarr Jaye, Yapei Chang, Mukund Rungta, Emmanuel Aboah Boateng, Sadid Hasan, Ehi Nosakhare, and Soundar Srinivasan.
\newblock {Auto-Eval Judge}: Towards a general agentic framework for task completion evaluation.
\newblock \emph{arXiv preprint arXiv:2508.05508}, 2025.

\bibitem{lu2024toolsandbox}
Jiarui Lu, Thomas Holleis, Yizhi Zhang, Bernhard Ber, Moritz Stephan, Hao Zhu, Subhajit Chaudhury, Akihiro Kishimoto, Radu Marinescu, Michael Muller, et al.
\newblock {ToolSandbox}: A stateful, conversational, interactive evaluation benchmark for {LLM} tool use capabilities.
\newblock \emph{arXiv preprint arXiv:2408.04682}, 2024.

\end{thebibliography}